Human tissue specific markers

### 2017-06-08 manuscript/manuscript.Rnw
update the latex headers
add tissue specific marker barplot

\documentclass[english,12pt]{article}
\usepackage{fontspec}
\setmainfont{FreeSerif}
\setsansfont{FreeSans}
\setmonofont{FreeMono}
\setmathrm{FreeSerif}
\setmathsf{FreeSans}
\setmathtt{FreeSerif}
\usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in,headheight=14pt]{geometry}
\usepackage{url}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage[bf]{caption}
\usepackage{rotating}
\usepackage{wrapfig}
\usepackage{booktabs}
\usepackage{float}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{amsmath}
\usepackage{acro}
\usepackage{array}
\usepackage{dcolumn}
\usepackage{adjustbox}
\usepackage{longtable}
\usepackage{pdflscape}
\usepackage[backend=biber,natbib=true,hyperref=true,citestyle=numeric-comp,style=nature,autocite=inline]{biblatex}
\addbibresource{references.bib}
\usepackage[noblocks,auth-sc]{authblk}
\usepackage[hyperfigures,bookmarks,colorlinks]{hyperref}
%\usepackage[hyperfigures,bookmarks,colorlinks,citecolor=black,filecolor=black,linkcolor=black,urlcolor=black]{hyperref}
% Floats at end for journals
% \usepackage[nolists,figuresfirst,nomarkers,heads,nofighead,notabhead]{endfloat}
% \AtBeginFigures{\section*{Figure Legends}\renewcommand{\efloatseparator}{\hbox{}}}
% \AtBeginTables{\section*{Tables}\renewcommand{\efloatseparator}{\mbox{}}}
\usepackage[nomargin,inline,draft]{fixme}
\newcommand{\DLA}[1]{\textcolor{red}{\fxnote{DLA: #1}}}
\usepackage[x11names,svgnames]{xcolor}
\usepackage{texshade}
\usepackage{tikz}
\usepackage{nameref}
\usepackage{xspace}
\usepackage[markifdraft,raisemark=0.01\paperheight,draft]{gitinfo2}
% this package will stretch the font slightly if necessary.
\usepackage{microtype}
\usepackage{zref-xr,zref-user}
\usepackage[capitalize]{cleveref}
\newenvironment{narrow}[2]{%
  \begin{list}{}{%
      \setlength{\topsep}{0pt}%
      \setlength{\leftmargin}{#1}%
      \setlength{\rightmargin}{#2}%
      \setlength{\listparindent}{\parindent}%
      \setlength{\itemindent}{\parindent}%
      \setlength{\parsep}{\parskip}}%
  \item[]}{\end{list}}
\def\newblock{\hskip}
\newenvironment{paperquote}{%
  \begin{quote}%
     \it
  }%
  {\end{quote}}
\renewcommand{\textfraction}{0.15}
\renewcommand{\topfraction}{0.85}
\renewcommand{\bottomfraction}{0.65}
\renewcommand{\floatpagefraction}{0.60}
%\renewcommand{\baselinestretch}{1.8}
\newenvironment{enumerate*}%
  {\begin{enumerate}%
    \setlength{\itemsep}{0pt}%
    \setlength{\parskip}{0pt}}%
  {\end{enumerate}}
\newenvironment{itemize*}%
  {\begin{itemize}%
    \setlength{\itemsep}{0pt}%
    \setlength{\parskip}{0pt}}%
  {\end{itemize}}
\oddsidemargin 0.0in 
\textwidth 6in
\raggedbottom
\clubpenalty = 10000
\widowpenalty = 10000
\setlength{\emergencystretch}{20em}
% make the afill smaller
\renewcommand\Affilfont{\itshape\small}
\renewcommand\cite[1]{\autocite{#1}}
\pagestyle{fancy}
\ExplSyntaxOn
\NewAcroCommand \gene {
  \group_begin:
    \keys_set:nn {acro} {short-format = \itshape}
    \acro_use:n{#1}
  \group_end:
}
\NewAcroCommand \protein { \acro_use:n {#1} }
\ExplSyntaxOff

@@

>>>>

\documentclass[english,12pt]{article}
\usepackage{fontspec}
\setmainfont{FreeSerif}
\setsansfont{FreeSans}
\setmonofont{FreeMono}
\setmathrm{FreeSerif}
\setmathsf{FreeSans}
\setmathtt{FreeSerif}
\usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in,headheight=14pt]{geometry}
\usepackage{url}
\usepackage{siunitx}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage[bf]{caption}
\usepackage{rotating}
\usepackage{wrapfig}
\usepackage{booktabs}
\usepackage{float}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{amsmath}
\usepackage[macros=false,single=true,single-form=long]{acro}
\usepackage{array}
\usepackage{dcolumn}
\usepackage[export]{adjustbox}
\usepackage{longtable}
\usepackage{pdflscape}
\usepackage[backend=biber,natbib=true,hyperref=true,citestyle=numeric-comp,style=nature,autocite=inline]{biblatex}
\addbibresource{references.bib}
\usepackage[noblocks,auth-sc]{authblk}
\usepackage[hyperfigures,bookmarks,colorlinks]{hyperref}
%\usepackage[hyperfigures,bookmarks,colorlinks,citecolor=black,filecolor=black,linkcolor=black,urlcolor=black]{hyperref}
% Floats at end for journals
% \usepackage[nolists,figuresfirst,nomarkers,heads,nofighead,notabhead]{endfloat}
% \AtBeginFigures{\section*{Figure Legends}\renewcommand{\efloatseparator}{\hbox{}}}
% \AtBeginTables{\section*{Tables}\renewcommand{\efloatseparator}{\mbox{}}}
\usepackage[nomargin,inline,draft]{fixme}
\newcommand{\DLA}[1]{\textcolor{red}{\fxnote{DLA: #1}}}
% \usepackage[x11names,svgnames]{xcolor}
\usepackage{texshade}
\usepackage{tikz}
\usepackage{nameref}
\usepackage{xspace}
\usepackage[markifdraft,raisemark=0.01\paperheight,draft]{gitinfo2}
% this package will stretch the font slightly if necessary.
%\usepackage{microtype}
\usepackage{zref-xr,zref-user}
\usepackage[capitalize]{cleveref}
\renewcommand{\textfraction}{0.15}
\renewcommand{\topfraction}{0.85}
\renewcommand{\bottomfraction}{0.65}
\renewcommand{\floatpagefraction}{0.60}
\oddsidemargin 0.0in 
\textwidth 6in
\raggedbottom
\clubpenalty = 10000
\widowpenalty = 10000
\setlength{\emergencystretch}{20em}
% make the afill smaller
\renewcommand\Affilfont{\itshape\small}
\renewcommand\cite[1]{\autocite{#1}}
\pagestyle{fancy}
\ExplSyntaxOn
\NewAcroCommand \gene {
  \group_begin:
    \keys_set:nn {acro} {short-format = \itshape}
    \acro_use:n{#1}
  \group_end:
}
\NewAcroCommand \protein { \acro_use:n {#1} }
\ExplSyntaxOff

@@

<<specific_markers_barplot,echo=FALSE,results="hide",warning=FALSE>>=
specific.markers.barplot <- function(tissue.name,genes) {
    setkey(interesting.gene.reads.wide,"gene_short_name")
    if (missing(genes))
        genes <- as.character(tissue.specific.genes[tissue==tissue.name,gene])
    tissue.specific.gene.reads <- 
        data.table(melt(interesting.gene.reads.wide[genes,],
                        id=c("gene_short_name","tracking_id"),
                        variable.name="tissue",
                        value.name="FPKM"
                        ))
    tissue.specific.gene.reads[,`log_2(FPKM)`:=log2(FPKM+1)]
    return(ggplot(tissue.specific.gene.reads,
                  aes(x=gene_short_name,
                      y=FPKM+1))
           + geom_violin()
           + scale_x_discrete("Gene")
           + scale_color_discrete("Tissue")
           + scale_shape_discrete("Tissue")
           + scale_y_log10()
           + geom_jitter(data=tissue.specific.gene.reads[order(-FPKM),
                                                        list(tissue=tissue[1:3],
                                                             max_fpkm=pmax(FPKM)[1:3]),
                                                        by=gene_short_name],
                        aes(y=max_fpkm+1,
                            x=gene_short_name,
                            color=capwords(as.character(tissue)),
                            shape=capwords(as.character(tissue))
                            ),
                        size=2
                        )
           + coord_flip()
           )
}
@
